### 2019-07-07 1-Preamble/4-Acknowledgement/acknowledgement.tex
Citations de Kaamelott pour le début de la thèse… ??

Of course on a more personal level, my thoughts are strongly dedicated to my family.
%
I first want to thank my \href{https://paris-sorbonne.academia.edu/FBesson}{older brother Florian}, who has always been my main model and who has been of a constant support during all my studies.
His rigour, dedication and seriousness kept pushing me further, and I am immensely proud of him.
Some of our board game nights were brain teasers comparable with some maths problems solved for this thesis!
% and I was happy to help him for the organization of the \href{http://lettres.sorbonne-universite.fr/Kaamelott}{research colloque}\footnote{~Un livre a aussi été publié suite \href{http://lettres.sorbonne-universite.fr/Kaamelott}{au colloque}, \href{https://www.editions-vendemiaire.com/catalogue/a-paraitre/kaamelott-un-livre-d-histoire-florian-besson-et-justine-breton-dir/}{``Kaamelott, un livre d'histoire'', aux éditions Vandémiaire}.} on the \emph{Kaamelott} french TV show in February 2017, it was \href{https://www.fabula.org/actualites/kaamelott-ou-la-relecture-de-l-histoire_75490.php}{the funniest} and \href{https://www.vousnousils.fr/2017/03/22/kaamelott-un-tremplin-vers-lhistoire-et-la-litterature-601428}{most exciting} \href{https://lpcm.hypotheses.org/10718}{research event} I have been to in the last four years!
%
I also thank my younger brother F., for being an inspiration for other (highly important) directions of my life. \emph{Ton courage et ta force m'inspirent quotidiennement, merci beaucoup !}
Very warm thanks then go to M. and my grand-parents, J. \& J.-M. and J., and to my uncle J. and aunt B.!
Finally, I thank sincerely my parents, C. and P., for being the best parents since the last $26$ years, and for their (vital) moral support.
\emph{Merci infiniment de nous avoir offert cette curiosité, merci d'être si gentils, et merci de votre soutien constant et de votre amour !}
\\
\indent
I would then like to thank my closest friends, sorted in chronological order of our first encounter in the \href{https://bulbapedia.bulbagarden.net/wiki/Tall_grass}{tall grass}\footnote{~Sorry if I forgot you, it's much harder to keep track of wild encounters in the tall grass in real wife, without a Pokédex! And due to space constraints, I had to choose quite arbitrarily whom to include\dots}: Guillaume, Florian, Marian, Hélène, Lucie, Lætitia and Julia in Briançon, Mayotte and Pierre in Marseille, Laurent, Simon, Tristan, Ludovic, Jessica, Romain, Benjamin, Angèle, Clément in Cachan, Jill-Jênn, Alain, Claire, Édouard, Loïc and Damien also in Cachan, Kumudham in India, Thibault, Sébastien, Sélim, Valentin again in Cachan, and Audrey, Rémi, Marine, Adrien, Bastien, Claire, Corentin and Lola in Rennes.
% In the last four years, thank you so much my dear friends, for great moments and an even greater moral support, for the holidays in India, Switzerland, Hungary/Austria, Strasbourg, Greece, Saint-Malo, Normandy, Scotland, Marseille, Madrid, Brittany etc. I loved traveling with you and hope to continue!
\emph{Une pensée particulière pour Hélène, merci pour ton énergie et ta détermination depuis 2018.}

>>>>

Of course on a more personal level, my thoughts are strongly dedicated to my family.
%
I first want to thank my \href{https://paris-sorbonne.academia.edu/FBesson}{older brother Florian}, who has always been my main model and who has been of a constant support during all my life and in my studies.
His rigour, dedication and seriousness kept pushing me further, and I am immensely proud of him.
Some of our board game nights were brain teasers comparable with some maths problems solved for this thesis!
% and I was happy to help him for the organization of the \href{http://lettres.sorbonne-universite.fr/Kaamelott}{research colloque}\footnote{~Un livre a aussi été publié suite \href{http://lettres.sorbonne-universite.fr/Kaamelott}{au colloque}, \href{https://www.editions-vendemiaire.com/catalogue/a-paraitre/kaamelott-un-livre-d-histoire-florian-besson-et-justine-breton-dir/}{``Kaamelott, un livre d'histoire'', aux éditions Vandémiaire}.} on the \emph{Kaamelott} french TV show in February 2017, it was \href{https://www.fabula.org/actualites/kaamelott-ou-la-relecture-de-l-histoire_75490.php}{the funniest} and \href{https://www.vousnousils.fr/2017/03/22/kaamelott-un-tremplin-vers-lhistoire-et-la-litterature-601428}{most exciting} \href{https://lpcm.hypotheses.org/10718}{research event} I have been to in the last four years!
%
I also thank my younger brother Fabian, for being an inspiration for other (highly important) directions of my life. \emph{Ton courage et ta force m'inspirent quotidiennement, merci beaucoup !}
Very warm thanks then go to M. and my grand-parents, J. \& J.-M. and J., and to my uncle J. and aunt B.!
Finally, I thank sincerely my parents, C. and P., for being the best parents since the last $26$ years, and for their (vital) moral support.
\emph{Merci infiniment de nous avoir offert cette curiosité, merci d'être si gentils, et merci de votre soutien constant et de votre amour !}
\\
\indent
I would then like to thank my closest friends, sorted in chronological order of our first encounter in the \href{https://bulbapedia.bulbagarden.net/wiki/Tall_grass}{tall grass}\footnote{~Sorry if I forgot you, it's much harder to keep track of wild encounters in the tall grass in real wife, without a Pokédex! And due to space constraints, I had to choose quite arbitrarily whom to include\dots}: Guillaume, Florian, Marian, Hélène, Lucie, Lætitia and Julia in Briançon, Mayotte and Pierre in Marseille, Laurent, Simon, Tristan, Ludovic, Jessica, Romain, Benjamin, Angèle, Clément in Cachan, Jill-Jênn, Alain, Claire, Édouard, Loïc and Damien also in Cachan, Kumudham in India, Thibault, Sébastien, Sélim, Valentin again in Cachan, and Audrey, Rémi, Marine, Adrien, Bastien, Claire, Corentin and Lola in Rennes.
% In the last four years, thank you so much my dear friends, for great moments and an even greater moral support, for the holidays in India, Switzerland, Hungary/Austria, Strasbourg, Greece, Saint-Malo, Normandy, Scotland, Marseille, Madrid, Brittany etc. I loved traveling with you and hope to continue!
\emph{Une pensée particulière pour Hélène, merci pour ton énergie et ta détermination depuis 2018.}
